Exploring probability distributions for bivariate temporal granularities

### 2019-11-25 main.Rmd
order fine tune till eq 7

**Definition:  Order** of a linear granularity can be comprehended as the level graininess associated with a linear granularity. If we consider two linear granularities G and H, such that $G \preceq H$, then H is of higher order than G.

**Notation:  Hierarchy table** Let $H_n: (G, C, k)$ be a hierarchy model containing n linear granularities. $G_{l}$ represents the linear granularity of order l and $k_{l,m}$ represents the period length of $G_{l}$ with respect to $G_{m}$ and $C_{G(l),G(m)}$ represents the circular granularity that relates linear granularity of order l and m, $\forall l,m \in n, l<m$.

In a hierarchy table, linear granularities are arranged from highest to lowest order of linear granularities.

@@

\begin{equation} \label{eq7}
\begin{split}
C_{(G_l,G_m)}(z) & = C_{(G_l,G_(l+1)}(z) + k(l, l+1)(C_{(G_(l+1),G_m)}(z)-1) \\  
  & =   C_{(G_l,G_(l+1)}(z) + k(l, l+1)[ C_{G_(l+1),G_(l+2)}(z) + k(l+1, l+2)( C_{G_(l+2), G_m)}(z) - 1) - 1]\\
  & =  C_{(G_l,G_(l+1)}(z) + k(l, l+1)(C_{G_(l+1),G_(l+2)}(z) - 1) + k(l, l+1)k(l+1, l+2)(C(l+2, m) - 1)\\
  & =  C_{(G_l,G_(l+1)}(z) + k(l, l+1)(C_{G_(l+1),G_(l+2)}(z) - 1) + k(l, l+2)(C_{G_(l+2),G_(l+m)}(z) - 1)\\
  &\vdots\\
  & = \sum_{i=0}^{m - l - 1} k(l, l+i)(C_{G_(l+i),G_(l+i+1)}(z) - 1)\\
\end{split}
\end{equation}

<!-- some discussions on primary units of calendar -->
**Example:** So far we have used the Gregorian calendar as it is the most widely used calendar. But it is far from being the only one. All calendars fall under three types - solar, lunar or lunisolar/solilunar but the day is the basic unit of time underlying all calendars. Various calendars, however, use different conventions to structure days into larger units: weeks, months, years and cycle of years. The French revolutionary calendar divided each day into 10 "hours", each "hour" into 100 "minutes" and each "minute" into 100 "seconds". Nevertheless, for any calendar a hierarchy can be defined. For example, in Mayan calendar, one day was referred to as 1 kin and the calendar was structured as follows:

@@

Let us use the equation \ref{eq:eq3} to compute the multiple-order-up granularity uinal_katun for Mayan calendar, which is periodic.

>>>>

**Definition:  Order** of a linear granularity can be comprehended as the level of graininess associated with a linear granularity. If we consider two linear granularities G and H, such that G is finer than or groups into H (by Definitions \ref{def:finerthan}, \ref{def:groupsinto}), then H is of higher order than G.

**Notation:  Hierarchy table** Let $H_n: (G, C, k)$ be a hierarchy model containing n linear granularities. $G_{l}$ represents the linear granularity of order l and $k(l,m)$ represents the period length of $G_{l}$ with respect to $G_{m}$ and $C_{G(l),G(m)}$ represents the circular granularity that relates linear granularity of order l and m, $\forall l,m \in n, l<m$.

In a hierarchy table, linear granularities are arranged from lowest to highest order of linear granularities.

@@

\begin{equation} \label{eq7}
\begin{split}
C_{(G_l,G_m)}(z) & = C_{G_l,G_{l+1}}(z) + k(l, l+1)(C_{(G_(l+1),G_m)}(z)-1) \\  
  & =   C_{(G_l,G_{l+1}}(z) + k(l, l+1)[ C_{G_{l+1},G_{l+2}}(z) + k(l+1, l+2)( C_{G_{l+2}, G_m}(z) - 1) - 1] \\
  & =  C_{(G_l,G_{l+1}}(z) + k(l, l+1)(C_{G_{l+1},G_{l+2}}(z) - 1) + k(l, l+1)k(l+1, l+2)(C_{G_{l+2}, G_{m}} - 1)\\
  & =  C_{(G_l,G_{l+1}}(z) + k(l, l+1)(C_{G_{l+1},G_{l+2}}(z) - 1) + k(l, l+2)(C_{G_{l+2},G_{l+m}}(z) - 1)\\
  &\vdots\\
  & = \sum_{i=0}^{m - l - 1} k(l, l+i)(C_{G_{l+i},G_{l+i+1}}(z) - 1)\\
\end{split}
\end{equation}

<!-- some discussions on primary units of calendar -->
**Example:** So far we have used the Gregorian calendar as it is the most widely used calendar. But it is far from being the only one. All calendars fall under three types - solar, lunar or lunisolar/solilunar but the day is the basic unit of time underlying all calendars. Various calendars, however, use different conventions to structure days into larger units: weeks, months, years and cycle of years. The French revolutionary calendar divided each day into 10 "hours", each "hour" into 100 "minutes" and each "minute" into 100 "seconds". Nevertheless, for any calendar a hierarchy can be defined. For example, in Mayan calendar, one day was referred to as 1 kin and the calendar was structured as follows (:

@@

Let us use the equation \ref{eq:eq3} to compute the multiple-order-up granularity uinal_katun for Mayan calendar, which is periodic and regular.
